ECML/PKDD 2016 Discovery Challenge \\ Bank Branch Visits and Customer Acquisition Prediction using Gradient Boosted Trees

### 2016-09-06 paper/paper.tex
updated

Since stacking index must be fixed in order to avoid leakage, we can only use either 2-folds or 10-folds stacking.
Although 10-folds is a common choice as it provides minimal information loss, we finally decided using 2-folds for two reasons:
\begin{enumerate}
 \item The training data is a combination data in two periods. If folds are split by time,
  stacking feature is built based on information from different time period, which is useful to avoid overfitting.

 \item Both stacking provides improvement on local CV, but 10 folds show discrepancy between CV and 30\% of testing data.
\end{enumerate}

In practice, a diversified combination of stacking features from different algorithms (KNN, RandomForest, SVM, NN, etc.)
will outperform stacking using only one algorithm.
Since we only used XGboost here, we compensated this by building several stacking features using randomized parameters to achieve diversification.

\textbf{Fig. 1} shows the AUC perfomance of Local 5-folds Cross Validation and 30\% of testing data using same parameters and seed.
 There is a strong correlation in AUC between Cross Validation and 30\% of testing data.
 The AUC improved once stacking is applied. We included more randomized stacking features until there is no improvement in AUC.

>>>>

Since stacking index must be fixed in order to avoid leakage, we can only use either 2-folds or 10-folds stacking.
Although 10-folds is a common choice as it provides minimal information loss, we finally decided using 2-folds for two reasons:
\begin{enumerate}
 \item The training data is a combination data in two different time periods. If folds are split by time,
  stacking feature is built based on information from another time period, which is useful to avoid overfitting.

 \item Both 2-folds and 10-folds stacking gives improvement on AUC, but 10-folds stacking shows
  discrepancy in improvement between Cross Validation and 30\% of testing data.
\end{enumerate}

In practice, a diversified combination of stacking features from different algorithms (KNN, RandomForest, SVM, NN, etc.)
will outperform stacking using only one single algorithm.
Since we only used XGboost here, we compensated this by building several stacking features using randomized parameters to achieve diversification.

\textbf{Fig. 1} shows the AUC perfomance of 5-folds Cross Validation and 30\% of testing data using same parameters and seed.
 There is a strong correlation in AUC between Cross Validation and 30\% of testing data.
 AUC is improved once stacking is applied and we included more randomized stacking feature until there is no improvement in AUC.
